Using Incremental Many-to-One Queries to Build a Fast and Tight Heuristic for A* in Road Networks

### 2021-11-15 paper/ch_potentials.tex
improve CH visualization
pseudo code improvements

@@

\begin{algorithm2e}
\KwData{$B[x]$: tentative distance from $x$ to target $t$}
\KwData{Minimum priority queue $Q$, also called open list, ordered by tentative distances}
$B[x] \leftarrow +\infty$ for all $x\neq t$;
$B[t] \leftarrow 0$\;
Make $Q$ only contain $t$ with weight $0$\;
\While{not $Q$ empty}{
	$y\leftarrow$ pop minimum element from $Q$\;
	\For{all down-edges $xy$ in $G^+_\ell$}{
		\If{$B[x] > w_\ell(xy) + B[y]$}{
			$B[x]\leftarrow w_\ell(xy) + B[y]$\;
                        Add $x$ or decrease $x$'s key in $Q$ to $B[x]$\;
		}
	}
}
\caption{CH backward search}
\label{algo:ch-backward}
\end{algorithm2e}

\begin{figure}
\centering
\includegraphics{fig/ch}
% TODO nicer fig
\caption{
Solid lines are edges in $G$. Dotted lines are shortcuts. Red is shortest $st$-path in $G$. Blue is equaly long up-down $st$-path in $G^+$. $m$ is the mid node.
}
\label{fig:ch}
\end{figure}

@@

@@

\begin{algorithm2e}
\KwData{$B[x]$: tentative distance from $x$ to $t$ as computed by Algorithm~\ref{algo:ch-backward}}
\KwData{$D[x]$: memoized distance from $x$ to $t$, $\bot$ initially}
\KwData{$P[x]$: parent node of $x$ in the elimination tree, parent of root is $\bot$}
\KwData{$S$: stack with nodes to compute distances, empty initially, only used to store intermediate data}
\SetKwFunction{Dist}{ComputeAndMemoizeDist}
\SetKwFunction{Push}{push}
\SetKwFunction{Pop}{pop}
\SetKw{Break}{break}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\Dist{$x$}}{
  \tcp{Determine for what nodes, the $D$ needs to be filled}
  $y \gets x$\;
	\While{$D[y] = \bot$}{
    $S$.\Push{$y$}\;
		\If{$P[y] = \bot$}{
      \Break\;
		}
    $y \gets P[y]$\;
  }
  \tcp{Fill $D$ for those nodes}
  \While{$S$ not empty}{
    $y \gets S$.\Pop{}\;
		$D[y]\gets B[y]$\;
		\For{all up-edges $yz$ in $G^+_\ell$}{
                        $D[y]\gets\min\{D[y],w_\ell(yz)+D[z]\}$\;
		}
	}
	\Return{$D[x]$}\;
}
\caption{Elimination tree based Lazy RPHAST algorithm}
\label{algo:cch_pot}
\end{algorithm2e}

>>>>

\usepackage{tikz}
\usetikzlibrary{automata,arrows,positioning,calc}
\tikzstyle{node}=[circle,inner sep=0.5mm,minimum size=6.5mm,draw = black]

@@

\begin{figure}
\centering
\begin{tikzpicture}[]
\tikzset{auto rotate/.style={to path={let \p1=(\tikztostart),\p2=(\tikztotarget),
\n1={atan2(\y2-\y1,\x2-\x1)},\n2={\n1-10},\n3={\n1+190}
in (\tikztostart.\n2) -- (\tikztotarget.\n3) \tikztonodes}}}

\node (s) at (0,0)     [node] {$s$};
\node (2) at (1.5,1.5) [node] {};
\node (3) at (3.7,1)   [node] {};
\node (4) at (5,3)     [node] {$m$};
\node (5) at (5.75,-0.1)  [node] {};
\node (6) at (6.75,1.2)   [node] {};
\node (7) at (7.75,-0.5)    [node] {};
\node (8) at (8.5,2)   [node] {};
\node (t) at (10,0.5)  [node] {$t$};

\draw[->] (-1,-1) -- (-1,3.5) node [midway, above, sloped] { rank };

\draw (s) edge[red, auto rotate] (2);
\draw[red] (2) -- (3);
\draw[red] (3) -- (4);
\draw[red] (4) -- (5);
\draw[red] (5) -- (6);
\draw[red] (6) -- (7);
\draw[red] (7) -- (8);
\draw (8) edge[red, auto rotate] (t);

\draw (2) edge[blue, auto rotate] (s);
\draw[blue, dashed] (2) -- (4);
\draw[blue, dashed] (4) -- (8);
\draw (t) edge[blue, auto rotate] (8);

\draw[dashed] (4) -- (6);
\draw[dashed] (6) -- (8);
\end{tikzpicture}
\caption{
Solid lines are edges in $G$. Dotted lines are shortcuts. Red is shortest $st$-path in $G$. Blue is equaly long up-down $st$-path in $G^+$. $m$ is the mid node.
}
\label{fig:ch}
\end{figure}

@@

\begin{algorithm2e}
\KwData{$B[x]$: tentative distance from $x$ to target $t$}
\KwData{Minimum priority queue $Q$, also called open list, ordered by tentative distances}
$B[x] \leftarrow +\infty$ for all $x\neq t$;
$B[t] \leftarrow 0$\;
Make $Q$ only contain $t$ with weight $0$\;
\While{$Q$ not empty}{
  $y\leftarrow$ pop minimum element from $Q$\;
  \For{all down-edges $xy$ in $G^+_\ell$}{
    \If{$B[x] > w_\ell(xy) + B[y]$}{
      $B[x]\leftarrow w_\ell(xy) + B[y]$\;
                        Add $x$ or decrease $x$'s key in $Q$ to $B[x]$\;
    }
  }
}
\caption{CH backward search}
\label{algo:ch-backward}
\end{algorithm2e}

@@

\begin{algorithm2e}
\KwData{$B[x]$: tentative distance from $x$ to $t$ as computed by Algorithm~\ref{algo:ch-backward}}
\KwData{$D[x]$: memoized distance from $x$ to $t$, $\bot$ initially}
\KwData{$P[x]$: parent node of $x$ in the elimination tree, parent of root is $\bot$}
\KwData{$S$: stack with nodes to compute distances, empty initially, only used to store intermediate data}
\SetKwFunction{Dist}{ComputeAndMemoizeDist}
\SetKw{Break}{break}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\Dist{$x$}}{
  \tcp{Determine for what nodes, the $D$ needs to be filled}
  $y \gets x$\;
	\While{$D[y] = \bot$}{
    Push $y$ onto $S$\;
		\If{$P[y] = \bot$}{
      \Break\;
		}
    $y \gets P[y]$\;
  }
  \tcp{Fill $D$ for those nodes}
  \While{$S$ not empty}{
    $y\leftarrow$ pop top element from $S$\;
		$D[y]\gets B[y]$\;
		\For{all up-edges $yz$ in $G^+_\ell$}{
                        $D[y]\gets\min\{D[y],w_\ell(yz)+D[z]\}$\;
		}
	}
	\Return{$D[x]$}\;
}
\caption{Elimination tree based Lazy RPHAST algorithm}
\label{algo:cch_pot}
\end{algorithm2e}
